Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-02 paper.tex
Some typos and British English revision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualization and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

@@

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimize production and to improve the publishing company profits or minimize losses \cite{Zhao2001}. This is the main objective of this paper.
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

@@

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a 'fuzzy-like' analysis, which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

@@

With this issue in mind, in this paper a data visualization and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print-run.
% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
% - análisis y extracción
% - predicción

@@

%********************************************************************************
\section{State of the art on sales forecasting} %FERGU: State of the art on sales forecasting?  ok  ;)
\label{sec:soa}

@@

This is the case of new book sales forecasting, a problem with issues such as 
dealing with quite limited data (just a few variables are known in advance) or the existence of several categorical values (which are harder to be processed). Given these issues, finding adequate forecasting techniques and selecting 
the best method to use is also a problem \cite{ChingChin2010}.
Moreover, in the case of new unpublished-books, there is no historical data to define patterns, and only some descriptive data about the new book are available 
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.

%This is the new book sales forecasting case, for which no historical data to make predictions is available \cite{ChingChin2010,FaderHardie2005,Madsen2008} and only some descriptive variables relative to the new unpublished-book are available.

%Forecasting sales of new books is a problem with issues such as dealing with limited data, finding adequate forecasting methods and selecting the best method to use \cite{ChingChin2010}.

%In the case of already published books, available historical data might help to generate predictive models.
%However, in the case of new books there is no historical data to define patterns, and only some descriptive data about the new book is available. 
%In these cases not any timeseries-based forecasting method can be used \cite{Madsen2008,ChernWSF15}.

%An additional issue is the difficulty to compare our model with classical forecasting methods, such as time series prediction methods, since books do not have specific sales time series.

For this reason, usually the methods used to predict book sales have been generally based on experts' experience. They analyze data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon et al. propose using the number of blog references as an indicator of the success of a book, and thus its sales. Different sales patterns are observed by analyzing data obtained.
% Antonio - describir esos 'sales patterns'. ;)
%
However, the authors used in these papers historical data from published books, 
%FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso.   ok
so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

Thus, taking into account the kind of problem we address in this paper, i.e. the prediction of sales of a new product for which no historical data is available, the classical forecasting methods based on time-series are not
adequate, although they can obviously be used once the book has been launched for sale. 
In our work the relevant variables in the prediction of sales are identified
by means of data visualization and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
In addition, since publishers need models to explain obtained predictions, 
`black box' forecasting methods may not be suitable, so models based on decision rules have been tested as an alternative.

@@

The main objective of this paper is to forecast sales for 
unpublished books for which no historical data is available. Instead, just some
descriptive and pre-sales known variables related to the new book. In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.

@@

\begin{minipage}{2.45in} \begin{verbatim}
reference
author
retail pricer
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim} \end{minipage}     &

@@

There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
In this work we have followed these steps:

\hspace{2cm}
\begin{verbatim}
  Step 1: Collect and analyse data
       - Data preprocessing
       - Feature selection
  Step 2: Select the best forecasting method
       - Evaluate forecasting models
       - Perform forecast
  Step 3: Subjectively adjust obtained results
      - Apply additional expert knowledge, such as information 
        about seasonality or trends.
\end{verbatim}

@@

The steps are described i the following paragraphs.

@@

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data are available in this problem).
% (Paloma) - Se deberían evitar paréntetis.

@@

SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organization, configures the output units into a topological representation of the original data. It tries to imitate the self-organization done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organize data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualize any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied for visualize natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recognizer.

This method is usually applied to analyze data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce. 
%FERGU: mencionarlo en la intro

@@

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretized. The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.

``Relief'' is the second evaluator used in this work. It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}. The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does. Also, it is applicable even working with both nominal and numeric features, without the need for transformations. For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbors, being these the nearest instance of the same class, and the nearest of the different class. Therefore, a good attribute is that which gives similar values fos instances of the same class, and different values for instances of different class.
  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator. With regard to the used search criteria, it is important to take into account that CFS evaluates attribute subsets, and Relief evaluates attributes separately.

@@

However, as in the case of new books only some descriptive data is available %FERGU: data es plural. is->are
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % eliminado el pie de página, es mejor usar referencias - JJ

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression}:
 Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictor) over the range of values in the dataset. 
In this statistical technique, data is modeled using linear functions to estimate 
unknown model parameters, examining the linear correlations between independent 
and dependent variables.

This method of regression provides an adequate and interpretable description of 
how the input affects the output as it models the dependent variable as a linear 
function of the independent variables. Moreover, the linear relation can be 
solved using the least squares method, that minimizes the error between the 
actual data and the regression line \cite{McClendon2015}.

@@

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximizing the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimizing the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

@@

The classification algorithm locates the nearest neighbour in instance space and 
assigns the class of that neighbour to the unknown instance.
In order to improve the robustness of the model, several neighbours can be 
located, assigning the resulting class to an unclassified vector using the 
closest k vectors found in the training set by majority vote.

@@

This model is a generalization of the standard linear perceptron that uses several 
layers of nodes (called neurons) and that is able to solve linearly inseparable 
problems \cite{SteinwenderBitzer2003}.
Each neuron consists of a linear combination of weighted inputs which is passed 
though a non-linear activation function to produce its output.

@@

The objective is finding the most appropriate forecasting method that minimizes 
the error between the obtained forecast and the actual sales for each new book 
published.

@@

In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance. In our experiments, the best value of $k$ in the $k$-nearest neighbor was empirically found at $k=3$. For SVM, the widely used Radial Basis Function (RBF) kernel is selected. As reported in several studies, RBF kernel has a reliable performance and can analyze higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel. We apply grid search which is the most common approach to find $C$ and $\gamma$. The best performance of SVM was found at $C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one hidden layer since it was proven in the literature that an MLP with one hidden layer can approximate any continuous or discontinuous function \cite{hornik1989multilayer,mirjalili2014let}. However, there is no rule of thumb on selecting the best number of neurons in the hidden layer. One suggested method that is followed in this work is to set the number of neurons in the hidden layer to $2 \times I + 1$ where $I$ is the number of inputs in the dataset \cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

@@

Once the methods to be applied have been chosen, they must be applied to datasets 
to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practice. %, limiting at the same time the overfitting problem.

@@

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

%*************************************** SOM ANALISYS
% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an exhaustive analisys of the SOM results was carried out in order to 
determine the best variables to be considered to buid the forecasting model.

Further important prepocessing steps are carried out before applying the SOM analysis.
First, in order to label the U-matrix with total-sales values, this variable is converted from numerical to categorical. Five categories have been created to represent the quantities of sales of each book: Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total-sales that correspond to each category along with the number of books that fall in. Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset. We can notice that most of 77\% of the book are categorized as VL and L with limited number of sales. On the other side, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder. The new categorical feature is used to replace the old numerical Total Sales feature in the SOM analysis.

@@

Second, two categorical features (i.e; Editorial and Collection) are removed from the analysis since they have large number of unique different values and therefore they are less informative. Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-bining) have more than 10\% missing values so they are removed also.

Finally, the resulted dataset consisted of ten features including the new Total Sales categorical feature. The SOM algorithm is trained based on the nine numerical variables while the new total-sales variable is used to label this data. The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantization error of 0.691 and topographic error of 0.046.

Figure \ref{fig:componentplanes} shows the U-matrix and component variables resulted from SOM training. The term component is used in SOM to refer to the features. The component planes in Figure \ref{fig:componentplanes} show the trend of values of the the prototype vectors of the SOM map units. These values are represented as colors. The colorbar on the right of each component plane shows the indication of each color. On the other side, the U-matrix on the top left corner shows the distances between the adjacent units. It is important to note that high values in the matrix indicates large distance between the units of the map. It can be noticed also that there are more hexagons in the U-matrix than component planes since the distances between units is also represented as hexagons.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

@@

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}. This is the main objective of this paper.
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

@@

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

@@

With this issue in mind, in this paper a data visualisation and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimise print-run.
% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
% - análisis y extracción
% - predicción

@@

%********************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}

@@

This is the case of new book sales forecasting, a problem with issues such as 
dealing with quite limited data (just a few variables are known in advance) or the existence of several categorical values (which are harder to be processed). Given these issues, finding adequate forecasting techniques and selecting 
the best method to use is also a problem \cite{ChingChin2010}.
Moreover, in the case of new unpublished-books, there are no historical data to define patterns, and only some descriptive data about the new book are available 
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.

For this reason, usually the methods used to predict book sales have been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon et al. propose using the number of blog references as an indicator of the success of a book, and thus its sales. Different sales patterns are observed by analysing data obtained.
% Antonio - describir esos 'sales patterns'. ;)
%
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

Thus, taking into account the kind of problem we address in this paper, i.e. the prediction of sales of a new product for which no historical data are available, the classical forecasting methods based on time-series are not
adequate, although they can obviously be used once the book has been launched for sale. 
In our work the relevant variables in the prediction of sales are identified
by means of data visualisation and feature selection methods. Then, machine learning techniques are applied to predict sales and to infer the ideal print-run of a book.
In addition, since publishers need models to explain obtained predictions, 
`black box' forecasting methods may not be suitable, so models based on decision rules have been tested as an alternative.

@@

The main objective of this paper is to forecast sales for 
unpublished books for which no historical data are available. Instead, just some
descriptive and variables known in advance related to the new book. In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.

@@

\begin{minipage}{2.45in} \begin{verbatim}
reference
author
retail price
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim} \end{minipage}     &

@@

There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
In this work we have followed these steps:
%\hspace{2cm}
\begin{verbatim}
  Step 1: Collect and analyse data
       - Data preprocessing
       - Feature selection
  Step 2: Select the best forecasting method
       - Evaluate forecasting models
       - Perform forecast
  Step 3: Subjectively adjust obtained results
      - Apply additional expert knowledge, such as information 
        about seasonality or trends.
\end{verbatim}

@@

@@

In general, historical data are used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data are available in this problem).
% (Paloma) - Se deberían evitar paréntetis.

@@

SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data. It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied for visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce. 
%FERGU: mencionarlo en la intro

@@

  The Correlation Feature Selection (CFS) method evaluates subsets of features/variables on the basis of the hypothesis made by Hall in \cite{Hall1998}, ``A  good  feature  subset  is  one  that  contains  features  highly  correlated  with
(predictive of) the class, yet uncorrelated with (not predictive of) each other''. This evaluator needs the numeric features to be transformed to nominal features first, by being discretised. The CFS evaluation function measures the ``merit'' of the subsets, which depend on the mean feature-class correlation, and the average feature-feature intercorrelation. In addition, the correlation is measured by three variations: the Minimum Description Length (MDL), the symmetrical uncertainty, and the ``relief''.

``Relief'' is the second evaluator used in this work. It is important to note that the relief method implemented in Weka is an updated version \cite{RobnikSikonja1997}, called RRELIEFF, of the original by Kira \& Rendell \cite{Kira1992}. The algorithm works by evaluating single attributes, and not whole subsets of attributes as CFS does. Also, it is applicable even working with both nominal and numeric features, without the need for transformations. For this algorithm, the weight of an attribute depends on the difference of an attribute value inside an instance with its neighbours, being these the nearest instance of the same class, and the nearest of the different class. Therefore, a good attribute is that which gives similar values for instances of the same class, and different values for instances of different class.
  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator. With regard to the used search criteria, it is important to take into account that CFS evaluates attribute subsets, and Relief evaluates attributes separately.

@@

However, as in the case of new books only some descriptive data are available %FERGU: data es plural. is->are
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods.

@@

 % weka.classifiers.functions.LinearRegression
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/LinearRegression.html
 \item \emph{Linear Regression}:
 Linear regression \cite{Cohen2003,Yan2009,Rencher2102} method models the 
relationship between a scalar dependent variable (outcome) and several independent 
variables (predictor) over the range of values in the dataset. 
In this statistical technique, data are modelled using linear functions to estimate unknown model parameters, examining the linear correlations between independent and dependent variables.

This method of regression provides an adequate and interpretable description of 
how the input affects the output as it models the dependent variable as a linear 
function of the independent variables. Moreover, the linear relation can be 
solved using the least squares method, that minimises the error between the 
actual data and the regression line \cite{McClendon2015}.

@@

In classification problems the algorithm searches for an optimal hyperplane 
that separates two classes, maximising the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

@@

The classification algorithm locates the nearest neighbour in instance space and 
assigns the class of that neighbour to the unknown instance.
In order to improve the robustness of the model, several neighbours can be 
located, assigning the resulting class to an unclassified vector using the 
closest $k$ vectors found in the training set by majority vote.

@@

This model is a generalisation of the standard linear perceptron that uses several 
layers of nodes (called neurons) and that is able to solve linearly inseparable 
problems \cite{SteinwenderBitzer2003}.
Each neuron consists of a linear combination of weighted inputs which is passed 
though a non-linear activation function to produce its output.

@@

The objective is finding the most appropriate forecasting method that minimises 
the error between the obtained forecast and the actual sales for each new book 
published.

@@

In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance. In our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. For SVM, the widely used Radial Basis Function (RBF) kernel is selected. As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel. We apply grid search which is the most common approach to find $C$ and $\gamma$. The best performance of SVM was found at $C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one hidden layer since it was proven in the literature that an MLP with one hidden layer can approximate any continuous or discontinuous function \cite{hornik1989multilayer,mirjalili2014let}. However, there is no rule of thumb on selecting the best number of neurons in the hidden layer. One suggested method that is followed in this work is to set the number of neurons in the hidden layer to $2 \times I + 1$ where $I$ is the number of inputs in the dataset \cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

@@

Once the methods to be applied have been chosen, they must be applied to the datasets to obtain the prediction models for each one. 
Later on, the models ability must be validated on non-previously seen data.
Specifically, instead of using the conventional validation strategy based on 
using a training set and later on a testing set (unknown data against which 
the model must be tested), a cross-validation technique \cite{Geisser1993,Kohavi1995,Devijver1982} 
has been used to estimate how accurately the predictive model will perform in 
practise. %, limiting at the same time the overfitting problem.

@@

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked attributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

@@

%*************************************** SOM ANALISYS
% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an exhaustive analysis of the SOM results was carried out in order to 
determine the best variables to be considered to build the forecasting model.

Further important preprocessing steps are carried out before applying the SOM analysis.
First, in order to label the U-matrix with total-sales values, this variable is converted from numerical to categorical. Five categories have been created to represent the quantities of sales of each book: Very Low (VL), Low (L), Medium (M), High (H) and Very High (VH). Table \ref{table:freq} shows the ranges of total-sales that correspond to each category along with the number of books that fall in. Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset. We can notice that most of 77\% of the book are categorised as VL and L with limited number of sales. On the other side, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder. The new categorical feature is used to replace the old numerical Total Sales feature in the SOM analysis.

@@

Second, two categorical features (i.e; Editorial and Collection) are removed from the analysis since they have large number of unique different values and therefore they are less informative. Moreover, four features (i.e; Subject1, Subject2, Subject3 and Book-binding) have more than 10\% missing values so they are removed also.

Finally, the resulted dataset consisted of ten features including the new Total Sales categorical feature. The SOM algorithm is trained based on the nine numerical variables while the new total-sales variable is used to label this data. The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.

Figure \ref{fig:componentplanes} shows the U-matrix and component variables resulted from SOM training. The term component is used in SOM to refer to the features. The component planes in Figure \ref{fig:componentplanes} show the trend of values of the prototype vectors of the SOM map units. These values are represented as colours. The colorbar on the right of each component plane shows the indication of each colour. On the other side, the U-matrix on the top left corner shows the distances between the adjacent units. It is important to note that high values in the matrix indicates large distance between the units of the map. It can be noticed also that there are more hexagons in the U-matrix than component planes since the distances between units is also represented as hexagons.
